PANCHANGE_data_preprocessing

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
PHQ baseline missingness per person chunk

#Missigness of questionnaire items
Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
```{r complete cases only}
all.items <- c(phq.items_prepan,
                phq.items_base,
                phq.items_retro,
                gad.items_prepan,
                gad.items_base,
                gad.items_retro,
                pcl.items_prepan,
                pcl.items_base,
                pcl.items_retro)

@@

```{r Exclusion of participants because of missing questionnaire items}
dim(dat.no.sex.no.age.no.ibd)
dat.no.sex.no.age.no.ibd.incomplete.phq.questionnaire <- dat.no.sex.no.gender.no.age.no.ibd %>%
  filter(!is.na(phq.items_prepan))

dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)

dim(dat.no.sex.no.age.no.ibd)[1]-dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)[1]

dat.no.sex.no.gender.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.gender.no.age.no.ibd
```

>>>>

##Missigness of questionnaire items
#PHQ - baseline
PHQ Missingness NAs per person - count and percentages
```{r Missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at baseline
           %in%
             phq.items_base]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_phq_base = 
      na_per_person_phq_base/9 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_base)
```

Missingness per item
```{r Missingness per item}
dat.no.sex.no.gender.no.age.no.ibd.miss <- as.data.frame(colnames(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items]))
colnames(dat.no.sex.no.gender.no.age.no.ibd.miss) <- "Items"
dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss <- colSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items]))
dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc <- dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss/nrow(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items])
table(dat.no.sex.no.gender.no.age.no.ibd.miss$Items, dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc)
summary(dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc)

ggplot(data = dat.no.sex.no.gender.no.age.no.ibd.miss,
       aes(x = Items, y = item.miss.pc)) +
  geom_point() +
  labs(title = "GLAD: PHQ",
    y ="Missingness per item") +
  theme_minimal() +
  coord_flip()
```

```{r count of people missing a number of items}
table(dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq)
```

Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
```{r complete cases only}
all.items <- c(phq.items_prepan,
                phq.items_base,
                phq.items_retro,
                gad.items_prepan,
                gad.items_base,
                gad.items_retro,
                pcl.items_prepan,
                pcl.items_base,
                pcl.items_retro)

@@

Missingness NAs per person - count and percentages
```{r DEM Missingness}
dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq <- rowSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,colnames(dat.no.sex.no.gender.no.age.no.ibd) %in% all.items]))
freq(dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq)

PHQ.cc$miss_pc_total.phq <- PHQ.cc$na.per.person.phq/PHQ.n.items
freq(PHQ.cc$miss_pc_total.phq)
```
